Explicit B-spline regularization in diffeomorphic image registration

### 2013-10-25 paper.tex
ENH: Getting stuff ready for submission.

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{SyN.pdf}
  \caption{Illustration of the greedy SyN formulation.  Given images
  $I_A$ and $I_B$, the symmetric set-up requires finding the two
  transform pairs $\left(\phi_1,\phi_1^{-1}\right)$
  $\left(\phi_2,\phi_2^{-1}\right)$ which map to/from
  the respective images to the midway point. During
  optimization, the update field at each iteration is
  determined from the metric field gradient taken at
  the midway point, i.e.
  $\nabla \Pi_{\sim} \left(I\circ\phi_1(0.5),J\circ\phi_2(0.5)\right)$.
  The full
  forward and inverse transforms are found through
  composition, i.e. $\phi=\phi_1 \circ \phi_2^{-1}$ and
  $\phi^{-1}=\phi_2 \circ \phi_1^{-1}$.
  }
  \label{fig:syn}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{templates.pdf}
  \caption{Canonical views for each of the five cohort-specific templates generated using
  the ANTs tools as described
  in \cite{avants2010}.   The pseudo-geodesic transform between subjects is created from 
  the composition of transforms to/from the relevant template.
  }
  \label{fig:templates}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\textwidth]{pseudo_geodesic.pdf}
  \caption{Illustration of generating a pseudo-geodesic for any two subjects
  within the MGH10 cohort.  Once the transforms between the
  template and each subject are calculated, the mapping between any two
  subjects is found by composition of forward and inverse transforms.  For
  example, in the MGH data set, the pseudo-geodesic transform to
  map Subject g4 to Subject g7 is found by composing the forward
  transform from g4 to the template with the inverse transform from the
  template to g7 (green dashed lines).
  }
  \label{fig:pseudo_geodesic}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{labels.pdf}
  \caption{Axial views of sample labelings for a member of each data set.  
  The second row consists of the original labelings with the third row being
  refined versions of those labelings using the MALF algorithm \cite{wang2012}.
  These refinements provide more consistency between labelings and improved
  comparative assessments between algorithms.
  }
  \label{fig:labels}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \begin{tabular}{ccccc}
  {} &
  \multicolumn{2}{c}{\bf Original labeling} & 
  \multicolumn{2}{c}{\bf MALF labeling} \\
  \rotatebox{90}{\qquad\,\, CUMC12} &
  \includegraphics[height=38mm]{versusCUMC.png} &
  \includegraphics[height=38mm]{synComparisonCUMC.pdf} &
  \includegraphics[height=38mm]{versusCUMCMALF.png} &
  \includegraphics[height=38mm]{synComparisonCUMCMALF.pdf} \\
  \rotatebox{90}{\qquad\quad IBSR18} &
  \includegraphics[height=38mm]{versusIBSR.png} &
  \includegraphics[height=38mm]{synComparisonIBSR.pdf} &
  \includegraphics[height=38mm]{versusIBSRMALF.png} &
  \includegraphics[height=38mm]{synComparisonIBSRMALF.pdf} \\
  \rotatebox{90}{\qquad\quad LPBA40} &
  \includegraphics[height=38mm]{versusLPBA.png} &
  \includegraphics[height=38mm]{synComparisonLPBA.pdf} &
  \includegraphics[height=38mm]{versusLPBAMALF.png} &
  \includegraphics[height=38mm]{synComparisonLPBAMALF.pdf} \\
  \rotatebox{90}{\qquad\quad MGH10} &
  \includegraphics[height=38mm]{versusMGH.png} &
  \includegraphics[height=38mm]{synComparisonMGH.pdf} &
  \includegraphics[height=38mm]{versusMGHMALF.png} &
  \includegraphics[height=38mm]{synComparisonMGHMALF.pdf} \\
  \rotatebox{90}{\qquad\quad MAL35} &
  \includegraphics[height=38mm]{versusMAL.png} &
  \includegraphics[height=38mm]{synComparisonMAL.pdf} &
  \includegraphics[height=38mm]{versusMALMALF.png} &
  \includegraphics[height=38mm]{synComparisonMALMALF.pdf} \\
  \end{tabular}
  \caption{Dice results for both algorithms for 
  each subject warped to every other subject using the pseudo-
  geodesic transform.  Each 
  row corresponds to one of the five data sets used for evaluation.
  For each data set we include a plotting of all individual label 
  Dice results by volume and a combined label box plotting.  The
  left and right halves show the results for MALF-derived and 
  original labelings, respectively.
  }
  \label{fig:dice}
\end{figure}

@@

\begin{figure}[htb]
  \centering
    \includegraphics[width=0.95\textwidth]{jacobianRange.pdf}
  \caption{Violin plots of the range of log Jacobian values 
           (95th\% - the 5th\%)  
           for all deformable
           transforms from each subject to its corresponding
           template.  B-spline SyN demonstrates a tendency 
           to produce a much
           greater range of log Jacobian values.
           }
  \label{fig:jacobian}
\end{figure}

>>>>

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{SyN.jpg}
  \caption{Illustration of the greedy SyN formulation.  Given images
  $I_A$ and $I_B$, the symmetric set-up requires finding the two
  transform pairs $\left(\phi_1,\phi_1^{-1}\right)$
  $\left(\phi_2,\phi_2^{-1}\right)$ which map to/from
  the respective images to the midway point. During
  optimization, the update field at each iteration is
  determined from the metric field gradient taken at
  the midway point, i.e.
  $\nabla \Pi_{\sim} \left(I\circ\phi_1(0.5),J\circ\phi_2(0.5)\right)$.
  The full
  forward and inverse transforms are found through
  composition, i.e. $\phi=\phi_1 \circ \phi_2^{-1}$ and
  $\phi^{-1}=\phi_2 \circ \phi_1^{-1}$.
  }
  \label{fig:syn}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{templates.jpg}
  \caption{Canonical views for each of the five cohort-specific templates generated using
  the ANTs tools as described
  in \cite{avants2010}.   The pseudo-geodesic transform between subjects is created from 
  the composition of transforms to/from the relevant template.
  }
  \label{fig:templates}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.75\textwidth]{pseudo_geodesic.jpg}
  \caption{Illustration of generating a pseudo-geodesic for any two subjects
  within the MGH10 cohort.  Once the transforms between the
  template and each subject are calculated, the mapping between any two
  subjects is found by composition of forward and inverse transforms.  For
  example, in the MGH data set, the pseudo-geodesic transform to
  map Subject g4 to Subject g7 is found by composing the forward
  transform from g4 to the template with the inverse transform from the
  template to g7 (green dashed lines).
  }
  \label{fig:pseudo_geodesic}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.95\textwidth]{labels.jpg}
  \caption{Axial views of sample labelings for a member of each data set.  
  The second row consists of the original labelings with the third row being
  refined versions of those labelings using the MALF algorithm \cite{wang2012}.
  These refinements provide more consistency between labelings and improved
  comparative assessments between algorithms.
  }
  \label{fig:labels}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \begin{tabular}{c}
  \includegraphics[width=0.95\textwidth]{evaluation.jpg}
  \end{tabular}
\end{figure}

%\begin{figure}[htb]
%  \centering
%  \begin{tabular}{ccccc}
%  {} &
%  \multicolumn{2}{c}{\bf Original labeling} & 
%  \multicolumn{2}{c}{\bf MALF labeling} \\
%  \rotatebox{90}{\qquad\,\, CUMC12} &
%  \includegraphics[height=38mm]{versusCUMC.png} &
%  \includegraphics[height=38mm]{synComparisonCUMC.pdf} &
%  \includegraphics[height=38mm]{versusCUMCMALF.png} &
%  \includegraphics[height=38mm]{synComparisonCUMCMALF.pdf} \\
%  \rotatebox{90}{\qquad\quad IBSR18} &
%  \includegraphics[height=38mm]{versusIBSR.png} &
%  \includegraphics[height=38mm]{synComparisonIBSR.pdf} &
%  \includegraphics[height=38mm]{versusIBSRMALF.png} &
%  \includegraphics[height=38mm]{synComparisonIBSRMALF.pdf} \\
%  \rotatebox{90}{\qquad\quad LPBA40} &
%  \includegraphics[height=38mm]{versusLPBA.png} &
%  \includegraphics[height=38mm]{synComparisonLPBA.pdf} &
%  \includegraphics[height=38mm]{versusLPBAMALF.png} &
%  \includegraphics[height=38mm]{synComparisonLPBAMALF.pdf} \\
%  \rotatebox{90}{\qquad\quad MGH10} &
%  \includegraphics[height=38mm]{versusMGH.png} &
%  \includegraphics[height=38mm]{synComparisonMGH.pdf} &
%  \includegraphics[height=38mm]{versusMGHMALF.png} &
%  \includegraphics[height=38mm]{synComparisonMGHMALF.pdf} \\
%  \rotatebox{90}{\qquad\quad MAL35} &
%  \includegraphics[height=38mm]{versusMAL.png} &
%  \includegraphics[height=38mm]{synComparisonMAL.pdf} &
%  \includegraphics[height=38mm]{versusMALMALF.png} &
%  \includegraphics[height=38mm]{synComparisonMALMALF.pdf} \\
%  \end{tabular}
%  \caption{Dice results for both algorithms for 
%  each subject warped to every other subject using the pseudo-
%  geodesic transform.  Each 
%  row corresponds to one of the five data sets used for evaluation.
%  For each data set we include a plotting of all individual label 
%  Dice results by volume and a combined label box plotting.  The
%  left and right halves show the results for MALF-derived and 
%  original labelings, respectively.
%  }
%  \label{fig:dice}
%\end{figure}

@@

\begin{figure}[htb]
  \centering
    \includegraphics[width=0.95\textwidth]{jacobianRange.jpg}
  \caption{Violin plots of the range of log Jacobian values 
           (95th\% - the 5th\%)  
           for all deformable
           transforms from each subject to its corresponding
           template.  B-spline SyN demonstrates a tendency 
           to produce a much
           greater range of log Jacobian values.
           }
  \label{fig:jacobian}
\end{figure}
